%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software \& Firmware Developer} % Job title
    {Labforge Inc.} % Organization
    {Waterloo, Ontario} % Location
    {May 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed neural network structures, criteria and optimization techniques, achieving good performance in the field.}
        \item {Authored new approaches to object re-identification and tracking, creating fast and robust software solutions.}
        \item {Improved inertial sensor code bases, running sensor processes as daemons on cameras.}
        \item {Worked collaboratively with a team to develop a reliable C/C++ state estimation engine for stereo camera tracking.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Advanced Researcher \& Firmware Developer} % Job title
    {Northern Digital Inc.} % Organization
    {Waterloo, Ontario} % Location
    {May 2018 - Sept. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Utilized problem-solving skills and successfully implemented data fusion algorithms on 3D guidance systems.}
        \item {Using creative skills, authored new data fusion algorithms for 3D guidance systems achieving NASA level TRL4.}
        \item {Worked collaboratively with a team to develop a C/C++ simulator for virtual reality 3D inertial data.}
%        \item {Developed Python libraries for sensor data fusion visualization and statistical analysis.}
%        \item {Demonstrated adaptability by reworking/porting platform specific C/C++ libraries to other ARM platforms.}
%        \item {Responsible for professional presentations to team members, broader research and development leaders demonstrating confidence.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Advanced Researcher \& Teaching Assistant} % Job title
    {McMaster University} % Organization
    {Hamilton, Ontario} % Location
    {May - Dec. 2015 \& May - Sept. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Demonstrated computer skills by developing embedded C/C++ software for safety critical systems.}
        \item {Exercised good organization skills by creating software documentation for system design.}
%        \item {Took on addition responsibility by preparing lessons for students and presentations for laboratories.}
%        \item {Friendly/outgoing to students especially when addressing their questions/concerns.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer \& Mechanical Repairman \& Shop Employee} % Job title
    {Emnor Mechanical Inc.} % Organization
    {Hamilton, Ontario} % Location
    {May - Sept. 2015 \& May - Sept. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Demonstrated good organization skills by developing an inventory management software for the company warehouse.}
        \item {Consistently applied attention to detail in managing company payroll, invoices and purchase orders.}
%        \item {Implemented technology skills by reverse engineering damaged parts and producing CAD drawings using the Faro Arm.}
%        \item {Demonstrated a strong work ethic by disassembling, repairing and reassembling centrifugal pumps.}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
