%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Startup Competition 1st Place} % Affiliation/role
    {McMaster Canada-Israel Startup Competition} % Organization/group
    {Hamilton, Ontario} % Location
    {June, 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Winner of the 2019 McMaster Canada-Israel Startup Competition.}
        \item {Designed and programmed numerous technologies to accurately automate patient fluid intake.}
        \item {Traveled to Tel Aviv, Israel to present technologies to companies, universities and nursing homes.}
        \item {Presented technologies to Canadian companies, universities and nursing homes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Hackathon Mentor} % Affiliation/role
    {Hack The North} % Organization/group
    {Waterloo, Ontario} % Location
    {Sept. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Assisted Hackathon groups with embedded system problems.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Club Member} % Affiliation/role
    {McMaster Sumobots} % Organization/group
    {Hamilton, Ontario} % Location
    {Jan. 2018 - April 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Gained experience working in a small group on embedded systems and embedded system IO.}
        \item {Worked with CAD software to develop controller casing.}
        \item {Competed against other groups in the final competition.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Community Helper} % Affiliation/role
    {Ronald McDonald House} % Organization/group
    {Hamilton, Ontario} % Location
    {Jan. 2017 - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Gained experience working with the community to help sick children indirectly.}
        \item {Assisted with cleaning the facility and baked desserts.}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
